% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\begin{center}
    {\huge Zhenwei Pan} \\ \vspace{2pt} 
\end{center}

\basicInfo{
  \email{seasons.poon@gmail.com} \textperiodcentered\ 
  \phone{(+86) 158-767-00020} \textperiodcentered\ }

\section{\faUser\ Profile}
\begin{itemize}
    \item Dedicated backend developer with 4 years of experience in architecting scalable solutions and integrating webservice APIs.
    \item Proficient in various programming languages and technologies, emphasizing Golang for effective and reliable software development.
    \item Adept at working with various database systems such as MySQL, Redis, and PostgreSQL, ensuring seamless data management and retrieval.
    \item Experienced in using middleware like Kafka for handling real-time data streaming and asynchronous communication, enhancing system scalability and performance.
    \item Proven track record in architecting and implementing technical solutions that drive business growth and improve operational efficiency.
    \item Strong communicator, skilled in translating complex technical concepts into actionable plans and build strong relationships with clients, suppliers, and cross-functional teams.
\end{itemize}


\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, Canada}{2025 -- Present}
\textit{Master student} in Electronics Engineering (EE), expected June 2026
\datedsubsection{\textbf{Neusoft Institute Guangdong}, Guangdong, China}{2015 -- 2019}
\textit{B.S.} in Software Engineering

\section{\faCogs\ Technical Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Golang, C++
  \item Database: MySQL, Redis, PostgreSQL
  \item Middleware: Kafka
  \item Version Control: Git
  \item Tools: Docker, Kubernetes, CI/CD tools
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Shenzhen Mishengxin Technology Co., Ltd.} Shenzhen, China}{Sep. 2021 -- Aug. 2025}
\role{Golang}{Backend Development Engineer}
\begin{onehalfspacing}
    Cross-border payment channel construction, payment notification system optimization, delay system design
\begin{itemize}
  \item Built a domestic and overseas integrated payment platform, aggregating major domestic (WeChat Pay, Alipay, UnionPay) and overseas payment channels (Google Wallet, Apple IAP), providing one-stop access and reconciliation services for domestic (Sam's Club) and overseas merchants (HOK, PUBG), significantly reducing their technical and financial reconciliation costs.
  \begin{itemize}
      \item Increased payment conversion rates by 80\% through innovative platform design.
  \end{itemize}
  \item Designed and constructed a webhook payment notification platform to ensure transaction stability, decoupling payment logic from notifications and enhancing overall system reliability.
  \begin{itemize}
      \item Increased the success rate of payment notifications to 99\%.
  \end{itemize}
  \item Engineered a delay system with a complaint freeze period to mitigate user circumvention of penalties.
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{Isoftstone Co., Ltd.} Shenzhen, China}{July. 2019 -- Sep. 2021}
\role{Golang}{Backend Development Engineer}
\begin{onehalfspacing}
    System design and functional development, black industry confrontation, data drive and effect verification
\end{onehalfspacing}
\begin{itemize}
  \item Created a content rating system from scratch for online content providers for both existing and new products, providing review, quality control, and statistical functions; enabled information filtering, quality information recommendation, and business updates
  \begin{itemize}
      \item Increased user engagement time from an average of less than 10 minutes to over 30 minutes.
  \end{itemize}
  \item Implemented a real-time strategy enforcement system to block intended targets and prevent unlawful economic activities in the informal sector; conducted a random sampling of data to evaluate and provide real-time accuracy and health metrics
  \begin{itemize}
      \item The trading price of QQ accounts increased by 10 times on the black market after implementing the system.
  \end{itemize}
  \item Developed a security platform for business content security; used data labelling and algorithms to target illegal and informal activities; stored and provided real-time access to extensive data sets
  \item Designed the system to handle up to ten million QPS during peak periods; implemented Cross-Zone Disaster
Recovery and Multi-Site High Availability on the Cloud
\end{itemize}



\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{20}}, Tencent Programming Contest }{Sep. 2022}
\datedline{\textit{Bronze Prize}, Award on ACM-ICPC(Guangxi, China) }{May. 2018}
\datedline{\textit{\nth{1} Prize}, Award on Lanqiao Cup }{Jun. 2018}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Languages: English - Fluent(IELTS-7.5), Mandarin - Native speaker, Cantonese - Native speaker
  \item Interests: Taekwondo
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
